Verifying Concurrent Search Structure Templates for C Programs using VST

### 2023-04-12 concurrency/CONCUR 2023/paper.tex
resolve William's comment

\begin{figure}[ht]
	\begin{subfigure}[t]{0.45\textwidth}
		\lstinputlisting[language=caml, style=myStyle]{lock_traverse.ml} 
		\caption{The \lstinline{traverse} method of the lock-coupling template algorithm written in an ML-like language \cite{krishna2019compositional} \wm{Shouldn't it be lock and then unlock?}}
		\label{traverse_lock_a}	
	\end{subfigure}\qquad
	\begin{subfigure}[t]{0.48\textwidth}
		\lstinputlisting[language=C, style=myStyle]{lock_traverse.c} 
		\caption{The \lstinline{traverse} method of the lock-coupling template algorithm written in C}
		\label{traverse_lock_b}
	\end{subfigure}
	\caption{The \lstinline{traverse} method of the lock-coupling template algorithms}
	\label{traverse_lock}
\end{figure}

@@

%% C implementation 
To implement the template algorithm, it is crucial to keep track of the lower and upper bounds of the keys present in the subtree rooted at the current node. Therefore, we have incorporated two new fields, \lstinline{min} and \lstinline{max}, into each node of type \lstinline{tree_t} in our C implementation. These fields store the lower and upper bounds of the keys, respectively. When a thread arrives at a node in search of the key $\texttt{k}$, it checks whether $\texttt{k}$ falls within the range of that node. If $\texttt{k}$ falls within the range, the thread continues by calling \lstinline{findNext} to find the new node. If $\texttt{k}$ does not fall within the range, the thread releases the lock and returns to the root node by assigning the pointer of the root to the pointer of the current node (lines 21-22 in Figure \ref{traverse_giveup_a}).

@@

The key to the verification of \texttt{traverse} function is the loop invariant for the top-level loop. We define the loop invariant for \texttt{traverse} function of lock-coupling style as follows: 
\begin{align*} &\mathsf{traverse\_inv}() \triangleq\ \exists\ (x\in \mathit{range})\land \texttt{R(pn->p)} \ast  \nodeboxrep(b,\mathit{g\_root})\ \ast \cdots 
\end{align*}

@@

>>>>

\begin{figure}[ht]
	\begin{subfigure}[t]{0.45\textwidth}
		\lstinputlisting[language=caml, style=myStyle]{lock_traverse.ml} 
		\caption{The \lstinline{traverse} method of the lock-coupling template algorithm written in an ML-like language \cite{krishna2019compositional} \wm{Shouldn't it be lock and then unlock?}}
		\than{I copied exactly the same from thesis of Krishna. However, in the their of proofs, they had lock before unlock like you said. Do we need to changed to fit with our context and their code?} 
		\label{traverse_lock_a}	
	\end{subfigure}\qquad
	\begin{subfigure}[t]{0.48\textwidth}
		\lstinputlisting[language=C, style=myStyle]{lock_traverse.c} 
		\caption{The \lstinline{traverse} method of the lock-coupling template algorithm written in C}
		\label{traverse_lock_b}
	\end{subfigure}
	\caption{The \lstinline{traverse} method of the lock-coupling template algorithms}
	\label{traverse_lock}
\end{figure}

@@

%% C implementation 
To implement the template algorithm, it is crucial to keep track of the lower and upper bounds of the keys present in the subtree rooted at the current node. Therefore, we have incorporated two new fields, \lstinline{min} and \lstinline{max}, into each node of type \lstinline{node_t} in our C implementation. These fields store the lower and upper bounds of the keys, respectively. When a thread arrives at a node in search of the key $\texttt{k}$, it checks whether $\texttt{k}$ falls within the range of that node. If $\texttt{k}$ falls within the range, the thread continues by calling \lstinline{findNext} to find the new node. If $\texttt{k}$ does not fall within the range, the thread releases the lock and returns to the root node by assigning the pointer of the root to the pointer of the current node (lines 21-22 in Figure \ref{traverse_giveup_a}).

@@

The key to the verification of \texttt{traverse} function is the loop invariant for the top-level loop. We define the loop invariant for \texttt{traverse} function of lock-coupling style as follows: 
\begin{align*} &\mathsf{traverse\_inv}() \triangleq\ \exists\ (\mathsf{k} \in \mathsf{range})\land \mathsf{R(pn->p)} \ast  \nodeboxrep(\mathsf{pn})\ \ast \cdots 
\end{align*}

@@

\begin{align*} 
	&\mathsf{traverse\_inv\_1}() \triangleq\ \exists\ (\mathsf{k} \in \mathsf{range})\land \mathsf{R(pn->p)} \ast  \nodeboxrep(\mathsf{pn})\ \ast \cdots 
	\\
	& \mathsf{traverse\_inv\_2}() \triangleq\ 
\end{align*}
